### 2023-02-22 paper-thesis/chapters/10-coc.tex
Start example

\section{An example}
\todo{Example}

>>>>

\section{An example}
In this section we will give an example of how to type check a program. The program we will type check is:
\begin{lstlisting}
let T = Type;
(\v: Type. v) T
\end{lstlisting}

The process that happens during type-checking is shown in figure \ref{fig:type-check-example}.
\begin{enumerate}
	\item First, we type-check the outermost expression \verb|Let| in an empty scope $s_0$. That rule states we have to type-check the let-bound value using the same scope, then it creates a \verb|NSubst| declaration in a new scope $s_1$, with which it type checks the body (which is here abbreviated as $b_0$).

	\item \todo{tododododood}
\end{enumerate}
